---
title: "Graphing the third degree polynomial"
author: "Mihai Chiriac"
date: "October 10, 2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Summary

"Graphing the third degree polynomial" is an application created in R using Shiny library for visualization of the third degree polynomial curve.
The application accept as input the following parameters:

- Number of points
- Coeficients a, b, c and d for the f(x) = a*x^3 + b*x^2 + c*x + d
- Confirmation for showing/hiding the title

Choosing different coeficients modifies the curve shape.

## Shiny architecture

Shiny has to different components:

- the client - runs in browser. It allows end user to input parameters, sends the information to server and renders the response.
- the server - runs in Shiny server. It receives the request from the browser, processes it and returns the response back. 

Usually a shiny application consists of two files:

- ui.R for the client
- server.R for the server

## Preparing the dataset

The presentation uses the same default values as ui.R

```{r cars, echo = TRUE}
  no_of_points <- 100
  minX<- -7
  maxX<- 7
  a<- 1
  b<- 2
  c<- 3
  d<- 4
  seq_step = (maxX-minX) / no_of_points
  dataX <- seq(minX, maxX, seq_step)
  dataY <- a* dataX^3 - b*dataX^2 + c*dataX + d
  func_title = paste("f(x) = ", 
                paste("(", paste(a, paste(") * x^3 + (", 
                paste(b, paste(") * x ^2 + (", 
                paste(c, paste(") * x + (", paste(d,")")))))))))
  main<-ifelse(TRUE, func_title,"")
  
```

## Ploting the function

```{r pressure}
plot(dataX, dataY, xlab = "X", ylab = "Y", main = main, panel.first = grid())
```

